Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-03-10 paper/SupMat.Rnw
modified part of the caption for the VKQ figure

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Maximum growth rate, cellular silicate content, and half sturation constant dependences on temperature.]
{Species maximum population growth rates, $V_i$ (a), half saturation constants for the dependence 
of growth rates on nutrient concentration, $K_i$ (b), and cellular silicate content, $Q_i$ (c) dependend on 
temperature in ways explored by \cite{Descamps_2005} and \cite{Ellner_2016, Ellner_2019} and 
pictured here. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is 
\emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated 
values and interpolations from \cite{Descamps_2005} and closed circles and solid lines indicate 
values and functions used by \cite{Ellner_2016, Ellner_2019} and in our analyses. The two sets of
estimates and functions coincide on (c).\label{fig:VKQ}}
\end{figure}
%***DAN: I added the last sentence indicating the two sets of data and functions coincide on (c), can you please
%check that and let me know if it's true, Jasmin?

>>>>

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[Maximum growth rate, cellular silicate content, and half sturation constant dependences on temperature.]
{Species maximum population growth rates, $V_i$ (a), half saturation constants for the dependence 
of growth rates on nutrient concentration, $K_i$ (b), and cellular silicate content, $Q_i$ (c) dependend on 
temperature in ways explored by \cite{Descamps_2005} and \cite{Ellner_2016, Ellner_2019} and 
pictured here. Species 1 is \emph{F. crotonensis}, shown in blue, and species 2 is 
\emph{C. pseudostelligera}, shown in red. Open circles and dashed lines indicate estimated 
values and interpolations from \cite{Descamps_2005} and closed circles and solid lines indicate 
values and functions used by \cite{Ellner_2016, Ellner_2019} and in our analyses. The two sets of
estimates and functions coincide on (c), except for right-most point for species 2. For that species,
data were not available for $Q$ at $24^\circ$ from the original study of \cite{Descamps_2005}; \cite{Ellner_2016, Ellner_2019}
assumed constancy of $Q_2$ for $t$ between $18^\circ$ and $24^\circ$.\label{fig:VKQ}}
\end{figure}
%***DAN: I added the last sentence indicating the two sets of data and functions coincide on (c), can you please
%check that and let me know if it's true, Jasmin?
